\thispagestyle{empty}

\section*{Declaration in lieu of oath}
I hereby solemnly declare that I have independently completed this work or, in the case of
group work, the part of the work that I have marked accordingly. I have not made use of the
unauthorised assistance of third parties. Furthermore, I have used only the stated sources or
aids and I have referenced all statements (particularly quotations) that I have adopted from the
sources I have used verbatim or in essence.\\

I declare that the version of the work I have submitted in digital form is identical to the printed
copies submitted.\\

I am aware that, in the case of an examination offence, the relevant assessment will be marked
as ‘insufficient’ (5.0). In addition, an examination offence may be punishable as an administrative offence (Ordnungswidrigkeit) with a fine of up to €50,000. In cases of multiple or otherwise
serious examination offences, I may also be removed from the register of students.\\

I am aware that the examiner and/or the Examination Board may use relevant software or
other electronic aids in order to establish an examination offence has occurred
\\

I solemnly declare that I have made the previous statements to the best of my knowledge and
belief and that these statements are true and I have not concealed anything.\\

I am aware of the potential punishments for a false declaration in lieu of oath and in particular
of the penalties set out in Sections 156 and 161 of the German Criminal Code (Strafgesetzbuch; StGB), which I have been specifically referred to.

\fbox{\begin{minipage}{\textwidth}
    \center{\bfseries Section 156 False declaration in lieu of an oath} \\
    Whoever falsely makes a declaration in lieu of an oath before an authority which is competent to administer such
    declarations or falsely testifies whilst referring to such a declaration incurs a penalty of imprisonment for a term
    not exceeding three years or a fine.\\
    \center{\bfseries Section 161 Negligent false oath; negligent false declaration in lieu of oath}\\
    (1) Whoever commits one of the offences referred to in Sections 154 to 156 by negligence incurs a penalty of
    imprisonment for a term not exceeding one year or a fine.
    (2) No penalty is incurred if the offender corrects the false statement in time. The provisions of Section 158 (2)
    and (3) apply accordingly.
    
    
    \end{minipage}}

    \vspace*{4em}\noindent
    \hfill%
    \begin{tabular}[t]{c}
      \rule{10em}{0.4pt}\\ Place,date
    \end{tabular}%
    \hfill%
    \begin{tabular}[t]{c}
      \rule{10em}{0.4pt}\\ Signature
    \end{tabular}%
    \hfill\strut
    \end{document}